{\small Filamentary transport in high-power H-mode conditions and in no/small-ELM regimes to predict heat and particle loads on PFCs for future devices}

### 2017-11-12 Meetings/GPMNov2017/gpm_november2017_topic21.tex
continue the GPM slides

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}

@@

\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_{t}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: We matched correctly the shape the parallel
        connection length L$_{\parallel}$ is modified consistently
      \item<1|only@1> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> AUG: We have comparable edge density and divertor neutral
        pressure even though pressure increase earlier at higher current
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        consistent variation of parallel connection length
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: Neutral compression is roughly constant between
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
      \item<6|only@6> TCV: This tendency is substantially confirmed at
        TCV where
        profiles  
      \item<7|only@7> TCV: This is consistent with onset of detachment
        (at least in intermediate and lower current)
      \item<8|only@8> AUG: While the general observation of increasing
        blob size with $\Lambda_{div}$ is confirmed there are no
        differences between the current
      \item<9|only@9> TCV: confirm the observation of AUG. 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

% \begin{frame}{Outline}
% 	\begin{itemize}
% 		\item Background 
% 		\item Plans (we will not make a detailed list of the
%                   proposal, we already tried to combine and summarize them)
% 		\item Discussion
% 	\end{itemize}	
% \end{frame}

>>>>

\begin{frame}{L-Mode analysis: I$_p$ scan at constant q$_{95}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantQ95}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantq95}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantQ95}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantQ95}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantQ95_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantQ95}}
    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantq95_samedensity}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantQ95}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantQ95}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantQ95}}

@@

\begin{frame}{L-Mode analysis: I$_p$ scan at constant B$_{t}$}
\Fontvi
  \vspace{-1cm}
  \begin{columns}    
  \begin{column}{0.65\textwidth}
    \centering{\includegraphics<1>[height=.8\textheight]{../../Experiments/AUG/analysis/pdfbox/EquilibraLparallelConstantBt}}
    \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/GeneralIpScanConstantBt}}
    \centering{\includegraphics<3>[height=\textheight]{../../Experiments/TCV/analysis/pdfbox/EquilibriaLparallelConstantBt}}
    \centering{\includegraphics<4>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CurrentScanConstantBt}}
    \centering{\includegraphics<5>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/IpConstantBt_Profiles_UsDiv}}
    \centering{\includegraphics<6>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/n0_CurrentScanConstantBt}}
    \centering{\includegraphics<7>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/IpConstantBt_samedensity}}
    \centering{\includegraphics<8>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesConstantBt}}
    \centering{\includegraphics<9>[width=\textwidth]{../../Experiments/AUG/analysis/pdfbox/BlobSizeCurrentScanConstantBT}}
    \centering{\includegraphics<10>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/LambdaSizeIpScanConstantBt}}

  \end{column}
  \begin{column}{0.35\textwidth}
    \begin{itemize}
      \item<1|only@1> AUG: We matched correctly the shape the parallel
        connection length L$_{\parallel}$ is modified consistently
      \item<1|only@1> AUG: The scan was performed with similar puffing rate (0.8-1
        MA) whereas we reduced it at lower current to avoid early disruption
      \item<2|only@2> AUG: We have comparable edge density and divertor neutral
        pressure even though pressure increase earlier at higher current
      \item<2|only@2> AUG: The total power (Ohmic plus NBI) was kept
        constant throughout the scan
      \item<3|only@3> TCV: We repeat the same excercise at TCV with a
        consistent variation of parallel connection length
      \item<4|only@4> TCV: no additional heating
        used. Nevertheless the difference in power crossing the separatrix
        is small
      \item<4|only@4> TCV: Neutral compression is roughly constant between
      \item<5|only@5> AUG: At comparable edge density Upstream profiles are
        different with the tendency to develop shoulder easier at
        lower current. \alert{We have flattening of the upstream
          profiles only when $\Lambda_{div}$ is well above one on all
          the profile}
        \item<6|only@6> Neutrals at lower current are substantially
          higher even with similar edge density profiles.
      \item<7|only@7> TCV: This tendency is substantially confirmed at
        TCV where
        profiles  
      \item<8|only@8> TCV: This is consistent with onset of detachment
        (at least in intermediate and lower current)
      \item<9|only@9> AUG: While the general observation of increasing
        blob size with $\Lambda_{div}$ is confirmed there are no
        differences between the current
      \item<10|only@10> TCV: confirm the observation of AUG. 
      \end{itemize}
    \end{column}
\end{columns}
\end{frame}

\begin{frame}{LSN \textit{vs} Double null on TCV}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \centering{\includegraphics<1>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/CompareTargetProfilesLSN-DN}}
      \centering{\includegraphics<2>[width=\textwidth]{../../Experiments/TCV/analysis/pdfbox/DNRadiation_58623}}
    \end{column}
    \begin{column}{0.5\textwidth}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{H-Mode effect of puffing location}

\end{frame}

\begin{frame}{H-Mode effect of cryopumps}

\end{frame}

\begin{frame}{Comments on different divertor geometry which can be explored}

\end{frame}

\begin{frame}{Program for 2018: AUG}
\end{frame}

\begin{frame}{Program for 2018: TCV}
\end{frame}

\begin{frame}{Program for 2018: MAST-U}
\end{frame}

%\begin{frame}{Outline}
% 	\begin{itemize}
% 		\item Background 
% 		\item Plans (we will not make a detailed list of the
%                   proposal, we already tried to combine and summarize them)
% 		\item Discussion
% 	\end{itemize}	
% \end{frame}
